FinalManuscript_DISCS_UG

### 2018-06-25 parts/02_relatedliterature.tex
Expanded section 2.1

In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$, a decryption function $\mathcal{D}$.

@@

In image processing, the typical image operations being done are intensity transformations which maps intensity values to another, using spatial filters to do operations such as edge detection and image blurring, and histogram processing and equalization.

@@

Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative \cite{gonzalez_digital_2008}. In this case, suppose the intensity levels of an image are within the range $\left[0, L-1\right]$, then image negation can be expressed by
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}

The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values \cite{gonzalez_digital_2008}. This has the general form
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant and $r \ge 0$.

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$. This is especially useful since many output devices such as printers and display devices follow the power law, and so correcting the power-law response on these devices in a process called \textit{gamma correction} ensures reproducibility and accuracy of images being displayed \cite{gonzalez_digital_2008}.

@@

Spatial filters are not only used for edge detection, but there are filters that do image blurring (such as Gaussian blur and box blur) and image sharpening.
% Should I put a table of other kernels too>

\subsection{Histogram Processing and Equalization}
\textbf{TO-DO}

\section{Related Work and Previous Implementations}
CryptoImg

@@

>>>>

In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{tilborg_encyclopedia_2005}. A \textit{plaintext} is text that can be easily understood by everybody. On the other hand, a \textit{ciphertext} is a result from encrypting the plaintext using an encryption key. The plaintext space consists of all the possible plaintexts.

There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}. In symmetric encryption, the key is used for both encryption and decryption. On the other hand, asymmetric encryption uses separate keys for encryption and decryption. The encryption key (also called \textit{public key}) is shared to everybody, while the decryption key (also called \textit{private key}) is kept secret. Because of this, there is no need to agree upon some secure key sharing protocols. Usually, the security of asymmetric cryptosystems relies on the intractability of certain computational problems, like the RSA depends on the difficulty of integer factorization, while ElGamal depends on the difficulty of the discrete logarithmic problem.

@@

In image processing, the typical image operations being done are intensity transformations which maps intensity values to another, and the use of spatial filters to do operations such as edge detection and image blurring.

@@

Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}. In this case, suppose the intensity levels of an image are within the range $\left[0, L-1\right]$, then image negation can be expressed by
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}

The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}. This has the general form
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant and $r \ge 0$.

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$. This is especially useful since many output devices such as printers and display devices follow the power law, and so correcting the power-law response on these devices in a process called \textit{gamma correction} ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.

@@

Spatial filters are not only used for edge detection, but there are filters that do image blurring (such as Gaussian blur and box blur) and image sharpening.
% Should I put a table of other kernels too?

\section{Related Work and Previous Implementations}
There has been work done regarding the implementation of 
CryptoImg

@@

\section{Summary}
